---
title: "W_UP Linear Model"
author: "kyarachelle King"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARMS Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)


```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

Scatter plot shows positive relationship between ARM and SIM.The equation of the is SIMS = -4.1+0.05*ARM. The adjusted R-square is 0.467. The residual standard error is 1.226, residual standard error is its standard deviation of each normal spread of errors any piont on the line.
  
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
newdata=data.frame(GRIP=94, ARM=88)
predict(model.1,newdata,interval = "prediction")
```



# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The equation for SIMS explained by ARM is SIMS= -4.1 + .0545* ARM
The scatterplot shoes tht there is a positive between SIMS and ARM.

The equation for SIMS explained by ARM is
SIMS=-4.1+.0545*ARM

```{r}
basicAA <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicAA + geom_point() + geom_smooth(method=lm)
```

The scatter plot shows a positive correlation between GRIP and SIM.

# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```



# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interval="prediction")
``` 
SIMS=-5.43+0.037 * ARM + 0.024 * GRIP

```{r}
anova(model.1,model.3)
```
The anova model 1 with model 3. The null hypothesis is no difference in the ability to predict SIMS. The alternative hypothesis is that there is no difference. The pvalue is 0.00005 this so small that the diffince is the ability to predict SIMS is not due ti chance. The adjusted R square and standard deviation of errors both indicate ARM + GRIP model is better. The prediction for ARM + GRIP model is a 0.15 and the 95% confidance interval is -2.1 to 2.4.





